---
title: "Socialism Index"
author: "Nick Warino"
date: "8/18/2022"
output: 
  html_document: 
    toc: yes
    toc_float: yes
editor_options: 
  chunk_output_type: console
  markdown: 
    wrap: 72
---

```{=html}
<style> # CSS styles
.table-hover > tbody > tr:hover { 
  background-color: #f4f442;
}
</style>
```

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
options("scipen"=1000000)

folder_names <- c("raw_data", 
                  "output_data", 
                  "rmd", 
                  "docs", 
                  "scripts")
sapply(folder_names, dir.create)
```

```{r}
library(rmarkdown) # Dynamic Documents for R
library(tidyverse) # Easily Install and Load the 'Tidyverse'
library(ggthemes) # Extra Themes, Scales and Geoms for 'ggplot2'
library(ggrepel) # Automatically Position Non-Overlapping Text Labels with 'ggplot2'
library(ggtext) # Improved Text Rendering Support for 'ggplot2'
library(devtools) # Tools to Make Developing R Packages Easier
library(tidylog) # Logging for 'dplyr' and 'tidyr' Functions
library(skimr) # Compact and Flexible Summaries of Data
library(lemon) # Freshing Up your 'ggplot2' Plots
library(ragg) # Graphic Devices Based on AGG
library(kableExtra) # Construct Complex Table with 'kable' and Pipe Syntax
library(here) # A Simpler Way to Find Your Files
library(annotater) # Annotate Package Load Calls
library(scales) # Scale Functions for Visualization
library(fredr) # An R Client for the 'FRED' API
library(OECD) # Search and Extract Data from the OECD
library(readsdmx) # Read SDMX-XML Data
```

# Search for Socialism Index variables from OECD
> Unless you know the exact code of the series you’re looking for, the best > way to start is by downloading a dataframe with all the available datasets > and their descriptions, and then run searches on it. The search string can > be a regular expression and is case-insensitive by default. - [OECD API R package](https://github.com/expersso/OECD)



```{r}
dataset_list <- get_datasets()
# search_dataset("glance", data = dataset_list)
```
search_dataset("glance", data = dataset_list)
```{r}
trade_union_density <- get_dataset(dataset = "TUD")
collective_bargaining_coverage <- get_dataset(dataset = "CBC")

filter_list <- list(c(), c("GLBF90_GDP"))
gov_net_worth_gdp <- get_dataset(dataset = "GOV_2021", filter = filter_list)
```



```{r}
TUD_structure <- get_data_structure("TUD")
CBC_structure <- get_data_structure("CBC")
GOV_2021_structure <- get_data_structure("GOV_2021")
```

